---
title: "Check and compare model results"
author: "Ayush"
format: pdf
---

In our previous conversation, Suman pointed out that the trendlines of the charts in the word document and the charts that I have generated are not identical. I checked, this is a correct observation. This means that the results of the model that I run is different than what Suman has generated. I am sharing the models for every figure so that Suman can compare mu results and see where I have gone wrong.

```{r include=FALSE}

# libraries ---------------------------------------------------------------

library(here)
library(haven)
library(tidyverse)

# load data ---------------------------------------------------------------

data_as_inclusicve <- read_dta(
  here("data/",
       "Alkire-Seth inclusive well-being data for graphs.dta")
)



```


## Figure 1 - Change in Average Attainment and Inclusivity premium


### Model 1  - Populaiton Weighted Linear Model

$$
y \sim x\beta_1 + e 
$$

$$
x = \text{Change in space average attainment per annum}
$$

$$
y = \text{Inclusivity premium W\_Sen per annum}
$$

```{r mod1}

mod_pop_weighted_linear <- lm(data = data_as_inclusicve,
                              formula = S_W_Sen_pa ~ d_attain_pa,
                              weights = population)

summary(mod_pop_weighted_linear)

```

__Coefficients__

```{r mod1_add_info}

mod_pop_weighted_linear$coefficients

```

__Fitted Values__

```{r mod1_add_info1}
mod_pop_weighted_linear$fitted.values
```

### Model 2 - Population weighted Quadratic fit


$$
y \sim x\beta_1 + x^2\beta_2 + e 
$$

$$
x = \text{Change in space average attainment per annum}
$$


$$
y = \text{Inclusivity premium W\_Sen per annum}
$$

```{r mod2}

mod_pop_weighted_quadratic <- lm(data = data_as_inclusicve,
                              formula = S_W_Sen_pa ~ d_attain_pa + I(d_attain_pa^2),
                              weights = population)

summary(mod_pop_weighted_quadratic)

```

__Coefficients__

```{r mod2_add_info}

mod_pop_weighted_quadratic$coefficients

```

__Fitted Values__

```{r mod2_add_info1}
mod_pop_weighted_quadratic$fitted.values
```



### Model 3  - Unweighted Quadratic fit


$$
y \sim x\beta_1 + x^2\beta_2 + e 
$$


$$
x = \text{Change in space average attainment per annum}
$$


$$
y = \text{Inclusivity premium W\_Sen per annum}
$$

```{r mod3}

mod_pop_unweighted_quadratic <- lm(
  data = data_as_inclusicve,
  formula = S_W_Sen_pa ~ d_attain_pa + I(d_attain_pa^2))

summary(mod_pop_unweighted_quadratic)

```

__Coefficients__

```{r mod3_add_info}

mod_pop_unweighted_quadratic$coefficients

```

__Fitted Values__

```{r mod3_add_info1}
mod_pop_unweighted_quadratic$fitted.values
```


## Figure 2 - Shared prosperity premiums and inclusivity premiums across 25 countries

### Model 1 - Population weighted quadratic fit

$$
y \sim x\beta_1 + x^2\beta_2 + e 
$$

$$
y = \text{Shared Prosperity premium}
$$


$$
x = \text{Inclusivity premium W\_Sen per annum}
$$

```{r mod4}

mod_pop_weighted_quadratic <- lm(data = data_as_inclusicve,
                              formula = inc_shr_pre ~ S_W_Sen_pa + I(S_W_Sen_pa^2),
                              weights = population)

summary(mod_pop_weighted_quadratic)

```

__Coefficients__

```{r mod4_add_info}

mod_pop_weighted_quadratic$coefficients

```

__Fitted Values__

```{r mod4_add_info1}
mod_pop_weighted_quadratic$fitted.values
```



### Model 2 - Unweighted quadratic fit


$$
y \sim x\beta_1 + x^2\beta_2 + e 
$$


$$
y = \text{Shared Prosperity premium}
$$


$$
x = \text{Inclusivity premium W\_Sen per annum}
$$

```{r mod5}

mod_pop_unweighted_quadratic <- lm(data = data_as_inclusicve,
                              formula = inc_shr_pre ~ S_W_Sen_pa + I(S_W_Sen_pa^2))

summary(mod_pop_unweighted_quadratic)

```

__Coefficients__

```{r mod5_add_info}

mod_pop_unweighted_quadratic$coefficients

```

__Fitted Values__

```{r mod5_add_info1}
mod_pop_unweighted_quadratic$fitted.values
```


## Figure 3 - Inclusivity premiums and absolute changes in the MPIs

### Model 1 - Population weighted quadratic fit



$$
y \sim x\beta_1 + x^2\beta_2 + e 
$$

$$
y = \text{Absolute change per annum in M0}
$$


$$
x = \text{Inclusivity premium W\_Sen per annum}
$$

```{r mod6}

mod_pop_weighted_quadratic <- lm(data = data_as_inclusicve,
                              formula = abs_M0_33_pa ~ S_W_Sen_pa + I(S_W_Sen_pa^2),
                              weights = population)

summary(mod_pop_weighted_quadratic)

```

__Coefficients__

```{r mod6_add_info}

mod_pop_weighted_quadratic$coefficients

```

__Fitted Values__

```{r mod6_add_info1}
mod_pop_weighted_quadratic$fitted.values
```



### Model 2 - Unweighted quadratic fit

$$
y \sim x\beta_1 + x^2\beta_2 + e 
$$


$$
y = \text{Absolute change per annum in M0}
$$


$$
x = \text{Inclusivity premium W\_Sen per annum}
$$

```{r mod7}

mod_pop_unweighted_quadratic <- lm(data = data_as_inclusicve,
                              formula = abs_M0_33_pa ~ S_W_Sen_pa + I(S_W_Sen_pa^2))

summary(mod_pop_unweighted_quadratic)

```

__Coefficients__

```{r mod7_add_info}

mod_pop_unweighted_quadratic$coefficients

```

__Fitted Values__

```{r mod7_add_info1}
mod_pop_unweighted_quadratic$fitted.values
```
